---
title: "redo_p8105_hw1_wch2124"
output: github_document
date: '2023-09-21'
---
## problem 1
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(moderndive)
data("early_january_weather")
nrow(early_january_weather)
ncol(early_january_weather)
mean(pull(early_january_weather, temp))

```
The variables are the characteristics of the weather in January in 2013, including hour, temperature, humidity, wind, precipitation, and visibility. It has 358 rows and 15 columns, with a mean temperature of 39.58212. 
```{r graph}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point(color='darkblue')
ggsave("p8105_hw1_wch2124.pdf")
```
The scatter plot shows that temperature overall increases over the course of the month of January. 

## problem 2 
```{r}
my_df = 
  tibble(
  vec_numeric = rnorm(10),
  vec_char = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
  vec_factor = factor(c("LOW", "HIGH", "LOW", "MEDIUM", "LOW","MEDIUM", "LOW", "MEDIUM", "MEDIUM", "LOW" )),
  vec_logical = vec_numeric > 0 
)
my_df
mean(pull(my_df))
```
the mean() function on its own does not find the mean of the data frame, but when you add the 'pull' function, it computes the mean to be 5.5
```{r eval = FALSE}
as.numeric(my_df$vec_factor)
```
the as.numeric function produced numerical values in place of my factor levels. this explains why we needed to use the 'pull' function to find the mean because it returns a column as a vector. 
